Space Matters: extending sensitivity analysis to initial spatial conditions in geosimulation models

### 2018-06-13 paper.tex
Update on Overleaf.

\author[a,b]{Juste Raimbault\corref{cor1}}
\author[c,d]{Cl{\' e}mentine Cottineau}
\author[e]{Marion Le Texier}
\author[f]{Florent Le N{\' e}chet}
\author[a]{Romain Reuillon}

\address[a]{UPS CNRS 3611 ISC-PIF, Paris, France}
\address[b]{UMR CNRS 8504 G{\'e}ographie-cit{\'e}s, Paris, France}
\address[c]{Centre for Advanced Spatial Analysis, University College London, UK}
\address[d]{UMR CNRS 8097 Centre Maurice Halbwachs, Paris, France}
\address[e]{UMR 6266 IDEES, Universit{\'e} de Rouen Normandie, France}
\address[f]{Université Paris-Est, Laboratoire Ville Mobilité Transport, Marne-la-Vallée, France}
%NB : mon affiliation "officielle" c'est : 
%Le Néchet, F., Université Paris-Est, Laboratoire Ville Mobilité Transport, UPEMLV : 5 boulevard Copernic, Cité Descartes F 77454 Marne-la-Vallée cedex 2 France

\cortext[cor1]{Corresponding author.}

@@

\email{juste.raimbault@polytechnique.edu}

>>>>

%\author[a,b]{Juste Raimbault\corref{cor1}}
%\author[c,d]{Cl{\' e}mentine Cottineau}
%\author[e]{Marion Le Texier}
%\author[f]{Florent Le N{\' e}chet}
%\author[a]{Romain Reuillon}
\author{}

%\address[a]{UPS CNRS 3611 ISC-PIF, Paris, France}
%\address[b]{UMR CNRS 8504 G{\'e}ographie-cit{\'e}s, Paris, France}
%\address[c]{Centre for Advanced Spatial Analysis, University College London, UK}
%\address[d]{UMR CNRS 8097 Centre Maurice Halbwachs, Paris, France}
%\address[e]{UMR 6266 IDEES, Universit{\'e} de Rouen Normandie, France}
%\address[f]{Université Paris-Est, Laboratoire Ville Mobilité Transport, Marne-la-Vallée, France}
%NB : mon affiliation "officielle" c'est : 
%Le Néchet, F., Université Paris-Est, Laboratoire Ville Mobilité Transport, UPEMLV : 5 boulevard Copernic, Cité Descartes F 77454 Marne-la-Vallée cedex 2 France

%\cortext[cor1]{Corresponding author.}

@@

%\email{juste.raimbault@polytechnique.edu}
